---
title: "Practical Functions: Practically Magic"
subtitle: "University of Auckland"
date: "21st March 2024"
author: "Nicholas Tierney"
institute: Telethon Kids Institute
format: 
  revealjs:
    theme: [blood, extra.scss]
    incremental: true
    slide-number: true
    show-slide-number: all
    footer: "talks.njtierney.com/ua2024"
editor: visual
execute: 
  echo: false
  warning: false
  cache: true
  freeze: true
---

```{r}
#| label: library
#| include: false
library(tidyverse)
library(knitr)
library(colorspace)
library(naniar)
library(visdat)
library(icons)
```

```{r}
#| label: source-r-files
#| echo: false
#| message: false
#| output: false
lapply(list.files(here::here("R"), full.names = TRUE), source)
```

```{r}
#| label: helpers
#| include: false

icons_fa <- icons::fontawesome
icon_box <- icon_style(icons_fa$solid$`box-open`, fill = "#f0a800")
icon_link <- icon_style(icons_fa$solid$link, fill = "#f0a800")
icon_twitter <- icon_style(icons_fa$brands$twitter, fill = "#f0a800")
icon_github <- icon_style(icons_fa$brands$github, fill = "#f0a800")
icon_plane <- icon_style(icons_fa$solid$`paper-plane`, fill = "#f0a800")


as_table <- function(...) knitr::kable(..., format='html', digits = 3)

theme_set(
  theme_grey(base_size = 16) +
  theme(
    legend.position = "bottom",
    plot.background = element_rect(fill = "transparent"),
    legend.background = element_rect(fill = "transparent")
  )
)

# **ni**ck's **pa**lette
nipa <- list(red = "#c03018",
             orange = "#f0a800",
             green = "#609048",
             purple = "#484878",
             light_purple = "#A3A3BB",
             light_green = "#AFC7A3",
             light_orange = "#F7D37F",
             light_red = "#DF978B",
             pale_purple = "#ECECF1",
             pale_green = "#D7E3D1",
             pale_orange = "#FBE9BF",
             pale_red = "#EFCBC4")

```

# Intro

# Background

Put More slides here.

::: notes
Speaker notes go here.
:::

# This next slide is an image

##  {background-image="images/IMAGE.png" background-size="contain"}

# Take homes

# Future Directions

::: {.fragment .fade-up}
-   More features
-   More features
-   More features
:::

# Test

# Thanks

::: columns
::: {.column width = "40%"}

-   Miles McBain
-   Nick Golding
-   Hadley Wickham
:::

::: {.column width = "40%"}

-   So many great people
-   So many great people
-   So many great people
-   So many great people

:::

::::

# Resources

-   So many things
-   So many things
-   So many things
-   So many things

# Colophon

-   Slides made using [quarto](https://github.com/quarto-dev/quarto)
-   Colours taken + modified from [lorikeet theme from ochRe](https://github.com/ropenscilabs/ochRe) [njtierney/njt-talks](github.com/njtierney/njt-talks) <!-- - Header font is **Josefin Sans** --> <!-- - Body text font is **Montserrat** --> <!-- - Code font is **Fira Mono** --> <!-- - template available:  -->

# Learning more

`r icon_box` [package link]()

`r icon_link` [talk link]()

`r icon_twitter` nj_tierney

`r icon_github` njtierney

`r icon_plane` nicholas.tierney\@gmail.com

# **End.**
